Protected Areas Practical

### 2024-11-27 tutorial/MSc_PA_practical_answers.Rmd
updated setwd

1. Go to https://github.com/KiranLDA/MSc_Protected_Areas
2. Click on the big green button 'CODE'.
3. Select 'Download ZIP'.
4. Save the file to your desktop.
5. Once opened unzip/extract all files in the ZIP file.
6. Then also unzip the rasters inside `data/data.zip` into the `data` folder.

@@

**Ignore this section unless you run into problems accessing files later (e.g. species.tif)**

>>>>

1. Go to https://github.com/KiranLDA/MSc_Protected_Areas
2. Click on the big green button 'CODE'.
3. Select 'Download ZIP'.
4. Save the file to your computer in your chosen location.
5. Once downloaded, unzip/extract all files in the ZIP file.

@@

## **Ignore this section unless you run into problems accessing files later (e.g. species.tif)**
